\documentclass[aps,prl,superscriptaddress,nofootinbib]{revtex4-2}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{placeins}
\usepackage{float}

\begin{document}

\title{Supplemental Material for ``Calibrated PTA Evidence Identifies Low-Frequency Curvature but Not a Unique Nanohertz Source''}

\author{Ran DUAN}
\email{duanran@nao.cas.cn}
\affiliation{National Astronomical Observatories, Chinese Academy of Sciences}
\date{\today}

\maketitle

\section*{S1. Data Products and Density Convention}

The analysis uses public NANOGrav 15-year data products
(arXiv:2306.16213), the NANOGrav 15-year noise analysis
(arXiv:2306.16214), the NANOGrav timing-data release paper
(arXiv:2306.16217), and the NANOGrav new-physics model-comparison paper
(arXiv:2306.16219).  Official NANOGrav/PTArcade model files were taken
from Zenodo DOI 10.5281/zenodo.8084351, and the official PTArcade
\texttt{ceffyl} density product from Zenodo DOI 10.5281/zenodo.10495907.
The cross-PTA bridge uses public posterior-summary spectral information
from PPTA DR3, NANOGrav 15yr, and EPTA+InPTA DR2.  It is not a full IPTA
timing-residual likelihood and is used only as a controlled
source-ranking stress test.

PTArcade model files return $h^2\Omega_\mathrm{GW}$.  The residual-density
conversion used for official templates is
\begin{equation}
\rho^2 =
\frac{(H_0/h)^2 h^2\Omega_\mathrm{GW}}
{8\pi^4 f^5 T_\mathrm{span}} .
\end{equation}
This conversion was checked against \nolinkurl{ptarcade.models_utils.omega2cross}
to relative precision below $5\times10^{-16}$.

\section*{S2. Evidence-Ablation Check}

Table~\ref{tab:ablation} isolates the ingredients that close the absolute
Bayes-factor gap for SIGW-Gaussian.

\begin{table}[H]
\caption{\label{tab:ablation}SIGW-Gaussian evidence-ablation check.}
\begin{ruledtabular}
\begin{tabular}{lccc}
Template/density & Baseline & $\ln\mathcal{B}$ & Residual \\
\hline
local template + local KDE & fixed-$\gamma$ SMBHB & $-1.590\pm0.154$ & $-5.633$ \\
official template + local KDE & PTArcade BHB prior & $+0.687\pm0.147$ & $-3.356$ \\
official template + official density & PTArcade BHB prior, seed 42 & $+4.225\pm0.173$ & $+0.182$ \\
official template + official density & PTArcade BHB prior, 5-config mean & $+4.520\pm0.185$ & $+0.477$ \\
\end{tabular}
\end{ruledtabular}
\end{table}

The ablation shows that replacing the spectrum alone is insufficient.  Matched
official template, official density, and matched BHB-prior baseline are needed
for sub-nat absolute-evidence reproduction.

\section*{S3. Official-Density Robustness}

Five dynesty configurations were used: \texttt{nlive=500}, \texttt{dlogz=0.1}
with seeds 42, 7, and 123; and \texttt{nlive=1000}, \texttt{dlogz=0.05} with
seeds 42 and 7.

\begin{table}[H]
\caption{\label{tab:robust}Official-density leading-model robustness.}
\begin{ruledtabular}
\begin{tabular}{lcccc}
Model & mean $\ln\mathcal{B}$ & published & mean residual & max residual \\
\hline
SIGW-Gaussian & $+4.520$ & $\ln(57)=+4.043$ & $+0.477$ & $0.694$ \\
SIGW-delta & $+3.930$ & $\ln(44)=+3.784$ & $+0.146$ & $0.387$ \\
Cosmic superstrings & $+3.558$ & $\ln(46)=+3.829$ & $-0.271$ & $0.491$ \\
\end{tabular}
\end{ruledtabular}
\end{table}

We therefore describe the reproduction as sub-nat rather than as uniformly
within $0.5$ nat, because the largest SIGW-Gaussian residual in the sweep is
$0.694$ nat.

\section*{S4. Priors and Model-Selection Rule}

Table~\ref{tab:priors} lists the priors used for the main official-density
comparisons.  Frequencies are in Hz.  The official cosmological-template priors
are those supplied in the public PTArcade/NANOGrav model files.  The curved
SMBHB controls were specified before running the official-density family sweep,
and all tested curved-SMBHB variants are reported in Table~\ref{tab:env}.  The
main Letter reports the best-performing tested representative of each
curvature class, not a search over unreported curves.

\begin{table}[H]
\caption{\label{tab:priors}Priors and selection rule for the main evidence rows.}
\begin{ruledtabular}
\begin{tabular}{p{0.17\textwidth}p{0.41\textwidth}p{0.28\textwidth}p{0.10\textwidth}}
Model/class & Parameters and priors & Rationale & Status \\
\hline
PTArcade BHB baseline & Gaussian prior on $(\log_{10}A,\gamma)$ with
$\mu=(-15.615,4.707)$, $C_{11}=0.2787$, $C_{22}=0.1242$,
$C_{12}=-0.00264$ & matched NG15 PTArcade SMBHB baseline & fixed \\
SIGW-Gaussian & $\log_{10}f_\mathrm{peak}\sim U[-11,-5]$,
width $\sim U[0.1,3]$, $\log_{10}A\sim U[-3,1]$ & official PTArcade
stochastic template & fixed \\
SIGW-delta & $\log_{10}f_\mathrm{peak}\sim U[-11,-5]$,
$\log_{10}A\sim U[-3,1]$ & official PTArcade stochastic template;
upper-bound variants are reported separately & fixed \\
Cosmic superstrings & $\log_{10}G\mu\sim U[-14,-6]$,
$\log_{10}P\sim U[-3,0]$ & official PTArcade superstring template & fixed \\
Environmental turnover & $\log_{10}A\sim U[-18,-11]$,
$\log_{10}f_\mathrm{bend}\sim U[-9.8,-7.0]$,
$\kappa\sim U[0.5,8]$, $\gamma=13/3$; variants change $\gamma$ or bend
range as listed in Table~\ref{tab:env} & SMBHB environmental-hardening
control motivated by arXiv:1211.5375 and arXiv:1505.07179 & fixed \\
Broken power law & $\log_{10}A\sim U[-18,-11]$,
$\log_{10}f_\mathrm{bend}\sim U[-10.0,-6.8]$,
$\delta\sim U[0,6]$, $\kappa\sim U[0.5,8]$, $\gamma=13/3$ &
phenomenological low-frequency suppression surrogate & fixed \\
Eccentricity-inspired & $\log_{10}A\sim U[-18,-11]$,
$\log_{10}f_e\sim U[-10.0,-6.8]$, $\beta\sim U[0,3]$,
$\gamma=13/3$ & phenomenological eccentricity-inspired suppression
surrogate & fixed \\
\end{tabular}
\end{ruledtabular}
\end{table}

\section*{S5. Curved SMBHB Control Family}

The curved-SMBHB controls were evaluated on the same official PTArcade
\texttt{ceffyl} density and against the same PTArcade BHB-prior baseline.  The
environmental-turnover row is the astrophysical control; the broken-power-law
and eccentricity-inspired rows are phenomenological low-frequency suppression
controls, not population-synthesis source claims.

\begin{table}[H]
\caption{\label{tab:env}Curved-SMBHB control evidence on the official-density scale.
The last column reports the thermodynamic-integration residual from the family
cross-check in Table~\ref{tab:tiqmc} relative to the corresponding
five-configuration dynesty mean; entries with ``--'' were not included in that
family cross-check.}
\begin{ruledtabular}
\begin{tabular}{lcccc}
Model & class & mean $\ln\mathcal{B}$ & sample std & family TI residual \\
\hline
eccentricity-inspired & ecc. & $+3.839$ & $0.043$ & $+0.056$ \\
broken power law & BPL & $+3.656$ & $0.154$ & $+0.063$ \\
env. fixed $\gamma=13/3$ & env. & $+3.453$ & $0.062$ & $+0.017$ \\
env. free $\gamma$ & env. & $+3.360$ & $0.202$ & -- \\
env. broad bend & env. & $+2.992$ & $0.142$ & -- \\
env. low bend & env. & $+2.666$ & $0.103$ & -- \\
\end{tabular}
\end{ruledtabular}
\end{table}

Three distinct curvature parameterizations fall in the same approximately
one-nat evidence tier as the leading cosmological rows: environmental
turnover, smooth broken-power-law curvature, and eccentricity-inspired
suppression.  The physical environmental control is $1.067$ nat below
SIGW-Gaussian but only $0.476$ nat below SIGW-delta and $0.104$ nat below
superstrings.  The environmental row is a physical SMBHB control; the
broken-power-law and eccentricity-inspired rows are phenomenological
low-frequency suppression controls.  This supports a family-level
source-identification degeneracy, not a new source-detection claim.

\section*{S6. Official Stochastic-Model Ranking}

Only official PTArcade files defining \texttt{spectrum(f, ...)} were evaluated.
PBH and ULDM files exposing \texttt{signal(toas, ...)} were skipped by design.

\begin{table}[H]
\caption{\label{tab:rank}Single-configuration official-density stochastic-model ranking.}
\begin{ruledtabular}
\begin{tabular}{lcc}
Model & dim & $\ln\mathcal{B}$ vs BHB prior \\
\hline
\texttt{sigw\_gauss} & 3 & $+4.616\pm0.174$ \\
\texttt{sigw\_delta} & 2 & $+4.098\pm0.171$ \\
\texttt{sigw\_box} & 3 & $+3.830\pm0.182$ \\
\texttt{super} & 2 & $+3.739\pm0.170$ \\
\texttt{meta\_ls} & 2 & $+3.677\pm0.181$ \\
\texttt{dw\_sm} & 4 & $+3.625\pm0.183$ \\
\texttt{meta\_l} & 2 & $+3.014\pm0.186$ \\
\texttt{pt\_bubble} & 6 & $+2.906\pm0.188$ \\
\texttt{igw} & 3 & $+2.881\pm0.188$ \\
\texttt{pt\_sound} & 6 & $+2.238\pm0.192$ \\
\texttt{dw\_ds} & 4 & $+0.474\pm0.192$ \\
\texttt{stable\_m} & 1 & $-1.394\pm0.159$ \\
\texttt{stable\_k} & 1 & $-1.477\pm0.158$ \\
\texttt{stable\_n} & 1 & $-1.572\pm0.158$ \\
\texttt{stable\_c} & 1 & $-1.608\pm0.157$ \\
\end{tabular}
\end{ruledtabular}
\end{table}

\section*{S7. SIGW-Delta Prior-Boundary Sensitivity}

\begin{table}[H]
\caption{\label{tab:prior}SIGW-delta peak-frequency prior-boundary scan.}
\begin{ruledtabular}
\begin{tabular}{lccc}
Prior & $\ln\mathcal{B}$ & $\Delta\ln\mathcal{B}$ & best-fit $\log_{10} f_\mathrm{peak}$ \\
\hline
$\log_{10}f_\mathrm{peak}\le -5$ & $+4.098\pm0.171$ & $+0.000$ & $-5.110$ \\
$\log_{10}f_\mathrm{peak}\le -4$ & $+4.300\pm0.171$ & $+0.203$ & $-4.148$ \\
$\log_{10}f_\mathrm{peak}\le -3$ & $+4.524\pm0.169$ & $+0.426$ & $-4.107$ \\
\end{tabular}
\end{ruledtabular}
\end{table}

The prior-boundary sensitivity is modest but should be disclosed because the
original SIGW-delta posterior is known to sit near the upper peak-frequency
prior boundary.

\section*{S8. Free-Spectrum Bin-Covariance Null Calibration}

\begin{table}[H]
\caption{\label{tab:car}Covariance null-calibration statistics.}
\begin{ruledtabular}
\begin{tabular}{lcc}
Statistic & observed & null $p$-value \\
\hline
max abs off-diagonal correlation & $0.227106$ & $0.00019996$ \\
mean abs off-diagonal correlation & $0.029916$ & $0.00019996$ \\
largest eigenvalue & $1.482627$ & $0.00019996$ \\
entropy effective rank & $13.781766$ & $0.00019996$ \\
participation effective rank & $13.555656$ & $0.00019996$ \\
signal modes above 1.2 MP edge & $1$ & $0.00019996$ \\
\end{tabular}
\end{ruledtabular}
\end{table}

The leading covariance mode is real against the independent-Gaussian null, but
the overall rank remains close to the full 14-bin rank.  This supports treating
bin covariance as a subdominant correction for the leading comparisons.

\begin{table}[H]
\caption{\label{tab:cov-proj}Model-level covariance-aware projection check.
The first two numeric columns are diagonal and covariance-aware quadratic
distances in the 14-bin projection diagnostic; the last column is the implied
$-\Delta\chi^2/2$ correction quoted in the main text.  These are projection
diagnostics, not replacement Bayes factors.}
\begin{ruledtabular}
\begin{tabular}{lccc}
Comparison & diagonal & covariance-aware & implied $\Delta\ln Z$ shift \\
\hline
SIGW-Gaussian vs SMBHB & $0.480151$ & $0.491693$ & $-0.005771$ \\
stable-string proxy vs SMBHB & $308.923326$ & $306.301428$ & $+1.310949$ \\
\end{tabular}
\end{ruledtabular}
\end{table}

\section*{S9. Chain Convergence and Failed-Chain Handling}

\begin{table}[H]
\caption{\label{tab:rhat}Hellings--Downs chain diagnostics.}
\begin{ruledtabular}
\begin{tabular}{lc}
Diagnostic & value \\
\hline
warm-chain $\log_{10}A$ & $-14.199\pm0.122$ \\
warm-chain $\gamma$ & $3.272\pm0.321$ \\
cold-chain $\log_{10}A$ & $-14.251\pm0.168$ \\
cold-chain $\gamma$ & $3.401\pm0.418$ \\
two-chain $\hat R(\log_{10}A)$ & $1.047$ \\
two-chain $\hat R(\gamma)$ & $1.047$ \\
\end{tabular}
\end{ruledtabular}
\end{table}

The hot-chain attempt is excluded from convergence diagnostics because it had
zero accepted jumps and remained at non-finite posterior metadata.

\section*{S10. Evidence Cross-Check}

The four main non-baseline evidence rows were cross-checked independently of
dynesty by evaluating the official-density likelihood on Sobol points in the
prior hypercube.  For each model we computed both the direct estimator
$\log Z=\log E_\mathrm{prior}[L]$ and the power-posterior thermodynamic
integration estimator
\begin{equation}
\log Z=\int_0^1 \langle \log L\rangle_\beta\,d\beta .
\end{equation}
The run used 16384 Sobol points per scramble, five independent scrambles, and
81 $\beta$ values.

\begin{table}[H]
\caption{\label{tab:tiqmc}Sobol-QMC thermodynamic-integration cross-check.
Rows marked ``main'' use the five-scramble main cross-check.  Rows marked
``family'' use the three-scramble curved-SMBHB family cross-check from
Table~\ref{tab:env}.}
\begin{ruledtabular}
\begin{tabular}{lcccc}
Model & subset & QMC direct $\ln\mathcal{B}$ & QMC TI $\ln\mathcal{B}$ & TI residual \\
\hline
SIGW-Gaussian & main & $+4.638\pm0.078$ & $+4.637\pm0.078$ & $+0.117$ \\
SIGW-delta & main & $+3.993\pm0.065$ & $+3.992\pm0.065$ & $+0.063$ \\
Cosmic superstrings & main & $+3.599\pm0.053$ & $+3.598\pm0.053$ & $+0.040$ \\
Env. SMBHB, fixed $\gamma$ & main & $+3.519\pm0.082$ & $+3.517\pm0.082$ & $+0.064$ \\
Ecc.-curved SMBHB & family & $+3.896\pm0.080$ & $+3.894\pm0.080$ & $+0.056$ \\
Broken-PL SMBHB & family & $+3.721\pm0.103$ & $+3.719\pm0.103$ & $+0.063$ \\
Env. SMBHB, fixed $\gamma$ & family & $+3.472\pm0.067$ & $+3.470\pm0.067$ & $+0.017$ \\
\end{tabular}
\end{ruledtabular}
\end{table}

The residuals are relative to the corresponding five-configuration dynesty
means used in the main Letter.  The two environmental rows are intentionally
separate: the main row belongs to the five-scramble cross-check, while the
family row belongs to the three-scramble family cross-check used for the
curved-SMBHB comparison.

\section*{S11. Cumulative Low-Frequency-Bin Driver}

The cumulative-bin scan uses the official PTArcade \texttt{ceffyl} density
with $N_\mathrm{bins}=4,6,8,10,12,14$ and the same PTArcade BHB-prior
baseline.  It quantifies how many low-frequency Fourier bins are needed to
approach the 14-bin source ranking.

\begin{table}[H]
\caption{\label{tab:bins}Cumulative-bin evidence saturation.  The cumulative-bin
scan uses the representative single configuration also used in
Table~\ref{tab:rank}; therefore the 14-bin values need not equal the
five-configuration means in the main Letter.}
\begin{ruledtabular}
\begin{tabular}{lccc}
Model & $\ln\mathcal{B}_{14}$ & first $N$ within 0.5 nat & $\Delta\ln\mathcal{B}_{6\to14}$ \\
\hline
SIGW-Gaussian & $+4.616$ & $10$ & $+2.052$ \\
SIGW-delta & $+4.098$ & $8$ & $+1.751$ \\
eccentricity-inspired curvature & $+3.981$ & $8$ & $+1.735$ \\
environmental turnover & $+3.814$ & $8$ & $+1.775$ \\
cosmic superstrings & $+3.739$ & $8$ & $+1.274$ \\
broken-power-law curvature & $+3.670$ & $10$ & $+1.469$ \\
\end{tabular}
\end{ruledtabular}
\end{table}

The lowest eight to ten Fourier bins therefore carry the source-ranking
information for these stochastic spectral templates.  This is a diagnostic of
the released free-spectrum likelihood, not a completeness statement for
time-domain PBH or ULDM signal classes.

\section*{S12. Cross-PTA Bridge Likelihood}

The bridge likelihoods are products of posterior-summary spectral
densities.  They are deliberately separated from the full timing-residual
problem so that they test only whether the public spectral summaries already
produce robust source identification.  We define
\begin{equation}
\ln\mathcal{L}_\mathrm{local3}
=\ln\mathcal{L}_\mathrm{PPTA}^{\rm loc}
+\ln\mathcal{L}_\mathrm{NG15}^{\rm loc}
+\ln\mathcal{L}_\mathrm{EPTA}^{\rm loc},
\end{equation}
and
\begin{equation}
\ln\mathcal{L}_\mathrm{hybrid3}
=\ln\mathcal{L}_\mathrm{PPTA}^{\rm loc}
+\ln\mathcal{L}_\mathrm{NG15}^{\rm off}
+\ln\mathcal{L}_\mathrm{EPTA}^{\rm loc}.
\end{equation}
The local terms use the same per-bin density construction for each public
free-spectrum summary.  Since the released free-spectrum priors are uniform in
$\log_{10}\rho_k$ over the retained range, these posterior densities are
proportional to likelihood factors up to model-independent constants.  The
official NANOGrav term uses the official PTArcade \texttt{ceffyl} density.  In
NG15-only comparisons, Bayes factors are reported relative to the PTArcade
BHB-prior baseline; in the bridge tables below, values are absolute log
evidences within each bridge likelihood and should be compared only through
within-bridge $\Delta\ln Z$.  All 11 bridge templates passed the local
posterior-summary adapters and the NANOGrav official-density
likelihood-evaluation adapter; only the rows marked below are official
PTArcade spectrum implementations.

Because only the NANOGrav term is anchored to the official PTArcade density,
\texttt{hybrid3} is an anchored source-ranking stress test rather than a fully
calibrated multi-PTA Bayes-factor scale.  This product neglects cross-PTA
correlations from shared pulsars, common GW-realization information, and
array-dependent noise-policy differences; it is therefore a source-ranking
stress test only.

\begin{table}[H]
\caption{\label{tab:bridge-models}Full bridge model list and calibration
status.  ``Official template'' means that the row uses a public PTArcade
\texttt{spectrum(f,...)} implementation; ``official-density adapter'' means
that the template can be evaluated on the NANOGrav official
\texttt{ceffyl} likelihood term used in the bridge.}
\begin{ruledtabular}
\begin{tabular}{lcccc}
Model & family & official template & official-density adapter & NG15 target \\
\hline
SMBHB-PowerLaw & Astro-simple & no & yes & no \\
SMBHB-Turnover & Astro-simple & no & yes & no \\
SMBHB-Env & Astro-curved & no & yes & no \\
SMBHB-BrokenPL & Astro-curved & no & yes & no \\
SMBHB-Eccentric & Astro-curved & no & yes & no \\
PBH-SIGW-Analytic & SIGW-like & no & yes & no \\
SIGW-Gaussian & SIGW-like & yes & yes & yes \\
SIGW-Delta & SIGW-like & yes & yes & yes \\
Cosmic-Superstrings & Cosmo-other & yes & yes & yes \\
DomainWall & Cosmo-other & no & yes & no \\
PhaseTransition-Total & Cosmo-other & no & yes & no \\
\end{tabular}
\end{ruledtabular}
\end{table}

\begin{table}[H]
\caption{\label{tab:bridge}Leading bridge evidence values.  Values are absolute
log evidences within the bridge likelihood, not Bayes factors relative to the
NANOGrav-only BHB baseline.}
\begin{ruledtabular}
\begin{tabular}{lcc}
Model & local3 $\ln Z$ & hybrid3 $\ln Z$ \\
\hline
Cosmic superstrings & $-62.594\pm0.109$ & $-154.377\pm0.109$ \\
SIGW-delta & $-62.711\pm0.110$ & $-154.469\pm0.109$ \\
PBH-SIGW analytic & $-62.774\pm0.114$ & $-154.550\pm0.114$ \\
SIGW-Gaussian & $-63.046\pm0.114$ & $-154.850\pm0.115$ \\
Ecc.-curved SMBHB & $-63.215\pm0.121$ & $-155.040\pm0.121$ \\
Broken-PL SMBHB & $-63.344\pm0.121$ & $-155.209\pm0.121$ \\
Env. SMBHB & $-63.527\pm0.123$ & $-155.316\pm0.123$ \\
\end{tabular}
\end{ruledtabular}
\end{table}

The hybrid3 ordering preserves the same qualitative tier as local3.  Relative
to the best tested hybrid3 template, SIGW-delta, PBH-SIGW analytic,
SIGW-Gaussian, eccentricity-inspired SMBHB curvature, broken-power-law SMBHB
curvature, and environmental SMBHB turnover sit at $-0.092$, $-0.173$,
$-0.472$, $-0.663$, $-0.832$, and $-0.939$ nat, respectively.

\begin{table}[H]
\caption{\label{tab:bridge-sequence}Sequential anchored bridge ablation.
Values are absolute log evidences within each bridge stage; deltas are relative
to the stage leader.}
\begin{ruledtabular}
\begin{tabular}{lccc}
Stage & leader & selected cosmological deltas & curved-SMBHB delta range \\
\hline
NG15-off & PBH-SIGW analytic & SIGW-Gaussian $-0.663$, strings $-1.788$ &
$[-1.954,-1.464]$ \\
NG15-off+PPTA-local & PBH-SIGW analytic & SIGW-delta $-0.089$, strings $-0.173$ &
$[-1.055,-0.762]$ \\
NG15-off+EPTA-local & PBH-SIGW analytic & SIGW-Gaussian $-0.558$, strings $-0.887$ &
$[-1.364,-1.004]$ \\
hybrid3 & cosmic superstrings & SIGW-delta $-0.092$, PBH-SIGW $-0.173$ &
$[-0.939,-0.663]$ \\
\end{tabular}
\end{ruledtabular}
\end{table}

The leader changes to cosmic superstrings only after both public local terms
are included with the official NANOGrav anchor.  The stable conclusion is not
the identity of that leader, but the order-unity compression of cosmological
templates and curved-SMBHB controls.

\section*{S13. Bridge Family Evidence}

Family evidences are computed as equal-weight prior-volume mixtures over the
tested representatives in each family,
\begin{equation}
Z_F=\frac{1}{N_F}\sum_{m\in F} Z_m .
\end{equation}
This prevents a family with more tested representatives from being rewarded
solely for having more rows.  These numbers are not a complete
marginalization over all realizations of a physical source class; they are
tested-representative family mixtures for the bridge model set in
Table~\ref{tab:bridge-models}.

\begin{table}[H]
\caption{\label{tab:bridge-family}Bridge family evidences.}
\begin{ruledtabular}
\begin{tabular}{lccc}
Tier & Family & all-representative $\ln Z_F$ & leave-one-leader-out $\ln Z_F$ \\
\hline
local3 & SIGW-like & $-62.833$ & $-62.901$ \\
local3 & Astro-curved & $-63.354$ & $-63.431$ \\
local3 & Cosmo-other & $-63.486$ & $-64.755$ \\
local3 & Astro-simple & $-63.840$ & $-64.130$ \\
hybrid3 & SIGW-like & $-154.610$ & $-154.689$ \\
hybrid3 & Astro-curved & $-155.182$ & $-155.261$ \\
hybrid3 & Cosmo-other & $-155.279$ & $-156.594$ \\
hybrid3 & Astro-simple & $-155.650$ & $-155.941$ \\
\end{tabular}
\end{ruledtabular}
\end{table}

In hybrid3, the curved-SMBHB family is only $0.572$ nat below the SIGW-like
family.  Removing the leading representative from each family preserves the
same qualitative conclusion: curved SMBHB spectra remain in the same
order-unity evidence tier as SIGW-like spectra.

\section*{S14. Bridge Robustness and Frequency Diagnostics}

The hybrid3 robustness sweep reran the three leading templates and
SIGW-Gaussian with independent seeds and a higher-live-point configuration.
The ranges over the three runs were $[-154.412,-154.348]$ for cosmic
superstrings, $[-154.601,-154.428]$ for SIGW-delta,
$[-154.571,-154.528]$ for PBH-SIGW analytic, and
$[-154.982,-154.850]$ for SIGW-Gaussian.  A separate Sobol-QMC
thermodynamic-integration check gave hybrid3 $\ln Z=-154.429$ for cosmic
superstrings, $-154.604$ for SIGW-delta, and $-154.666$ for PBH-SIGW
analytic.  These checks preserve the non-discrimination message.

\begin{table}[H]
\caption{\label{tab:gamma-bridge}Effective low-frequency spectral-index
projection for the three curved-SMBHB controls.}
\begin{ruledtabular}
\begin{tabular}{lccc}
Model & PPTA DR3 & NANOGrav 15yr & EPTA+InPTA DR2 \\
\hline
Ecc.-curved SMBHB & $3.729^{+0.330}_{-0.320}$ &
$3.807^{+0.294}_{-0.301}$ & $4.022^{+0.199}_{-0.248}$ \\
Broken-PL SMBHB & $3.781^{+0.351}_{-0.332}$ &
$3.866^{+0.312}_{-0.332}$ & $4.103^{+0.184}_{-0.328}$ \\
Env. SMBHB & $3.720^{+0.303}_{-0.320}$ &
$3.814^{+0.284}_{-0.312}$ & $4.087^{+0.197}_{-0.328}$ \\
\end{tabular}
\end{ruledtabular}
\end{table}

The projection supports frequency-window curvature but should not be read as a
claim that the reported PTA spectral-index differences are fully
astrophysical.  The frequency-cut diagnostic similarly shows
non-identification: with $f\le5$, 8, 12, and 20 nHz, PBH-SIGW analytic leads
the reduced-bin hybrid diagnostic, while the all-bin diagnostic returns cosmic
superstrings and SIGW-delta at the top with curved-SMBHB controls within
about one nat.  Because this is a lower-live-point diagnostic, the main Letter
uses it only to identify the frequency window driving the ranking.

\section*{S15. Final Stability Diagnostics}

The final stability diagnostics consolidate completed runs rather than adding
new evidence calculations.  They test whether the title-level statement can be
supported by low-dimensional posterior-summary quantities and by the known
calibration/systematic budget.

\begin{table}[H]
\caption{\label{tab:final-ppc}Posterior-summary low-frequency predictive
diagnostic for the leading families.  Residuals are absolute median residuals
in units of the corresponding LUT standard deviation; this is not a
timing-residual PPC.}
\begin{ruledtabular}
\begin{tabular}{lccc}
Family & mean low-4 & max low-4 & mean high-bin \\
\hline
Astro-curved & $0.462$ & $1.617$ & $0.923$ \\
Cosmo-other & $0.478$ & $1.559$ & $0.911$ \\
SIGW-like & $0.465$ & $1.646$ & $0.914$ \\
\end{tabular}
\end{ruledtabular}
\end{table}

The comparable low-four-bin residuals support the restricted interpretation
that current public spectral summaries identify a low-frequency-curvature
feature shared by several tested families, not a unique source label.

\begin{table}[H]
\caption{\label{tab:final-budget}Evidence and systematic scales relevant to
source-identification interpretation.}
\begin{ruledtabular}
\begin{tabular}{lcc}
Effect & size (nat) & scope \\
\hline
official-density reproduction residual & $0.694$ & max single-config residual \\
SIGW-delta prior boundary & $0.426$ & tested upper-bound scan \\
dynesty/QMC-TI residual, main rows & $0.117$ & independent cross-check \\
dynesty/QMC-TI residual, curved rows & $0.063$ & curved-family cross-check \\
hybrid3 seed/live range & $0.173$ & bridge robustness sweep \\
SIGW-Gaussian minus best curved-SMBHB & $0.681$ & NG15 official scale \\
SIGW-like minus Astro-curved family & $0.572$ & hybrid3 family mixture \\
\end{tabular}
\end{ruledtabular}
\end{table}

Thus the remaining leading-model and family gaps are comparable to identified
calibration, prior-boundary, and bridge-robustness scales.

\begin{table}[H]
\caption{\label{tab:env-prior-final}Environmental-turnover prior sensitivity on
the official-density scale.  Gaps are relative to the listed cosmological row.}
\begin{ruledtabular}
\begin{tabular}{lcccc}
Environmental row & $\ln B$ & SIGW-Gauss. gap & SIGW-delta gap & string gap \\
\hline
fixed $\gamma=13/3$ & $3.453$ & $1.067$ & $0.476$ & $0.104$ \\
free $\gamma$ & $3.360$ & $1.160$ & $0.570$ & $0.197$ \\
broad bend prior & $2.992$ & $1.527$ & $0.937$ & $0.565$ \\
low-bend prior & $2.666$ & $1.854$ & $1.264$ & $0.892$ \\
\end{tabular}
\end{ruledtabular}
\end{table}

The environmental turnover is the physical SMBHB control in this set; the
broken-power-law and eccentricity-inspired rows are phenomenological curvature
controls.  The environmental-prior variants remain competitive with at least
part of the leading cosmological tier, but this is not a complete
population-synthesis marginalization.

\section*{S16. PTArcade/ceffyl Version and Plateau Diagnostic}

The official-density calculations used PTArcade version \texttt{1.1.5},
\texttt{ceffyl} version \texttt{1.41.2}, and the density archive
\texttt{PTArcade\_ceffyl\_0.2.0/ng15\_30f\_fs\{hd\}\_ceffyl}.  We checked
512 equal-weight posterior samples for each leading calibrated row against the
official density grid.  The lower-boundary and upper-boundary fractions were
zero for SIGW-Gaussian, SIGW-delta, cosmic superstrings, eccentricity-inspired
SMBHB curvature, broken-power-law SMBHB curvature, and environmental SMBHB
turnover.

\begin{table}[H]
\caption{\label{tab:plateau}Official-density grid-boundary diagnostic for the
leading calibrated rows.  The common grid range is
$[-15.101,-0.900]$ in $\log_{10}\rho$.}
\begin{ruledtabular}
\begin{tabular}{lccc}
Model & lower fraction & upper fraction & sampled $\log_{10}\rho$ range \\
\hline
SIGW-Gaussian & $0.000000$ & $0.000000$ & $[-9.012,-6.039]$ \\
SIGW-delta & $0.000000$ & $0.000000$ & $[-8.859,-6.104]$ \\
Cosmic superstrings & $0.000000$ & $0.000000$ & $[-8.782,-6.044]$ \\
Ecc.-curved SMBHB & $0.000000$ & $0.000000$ & $[-8.716,-6.035]$ \\
Broken-PL SMBHB & $0.000000$ & $0.000000$ & $[-8.654,-6.010]$ \\
Env. SMBHB & $0.000000$ & $0.000000$ & $[-8.762,-6.082]$ \\
\end{tabular}
\end{ruledtabular}
\end{table}

This diagnostic does not assert that all possible PTArcade/ceffyl likelihood
settings are plateau-free; it records that the leading rows used in this
Letter do not hit the official grid boundaries in the checked posterior-sample
region.

\section*{S17. Timing-Level Production and Development Gates}

These timing-level checks are development diagnostics only.  They use an
NG15-priority deduplicated reduced 87-pulsar namespace, with 67 NG15,
5 EPTA, and 15 PPTA pulsars retained and 36 duplicate occurrences skipped.
This object is not a public five-PTA direct combination.  The manifest is
recorded in \nolinkurl{results/5pta_timing/manifest_v2_ng15_priority_dedup_3array_development_2026-04-24.csv}.
The corresponding unique-only diagnostic retains 61 pulsars after excluding
all names occurring in more than one array.

All free-red, selected-red, and grouped-red timing-level routes remain below
the evidence-claim threshold because they failed the predeclared convergence
gate.  Fixed-red duplicate-priority diagnostics were stable in the two shared
GWB parameters, but higher-basis fixed-red tests did not pass the same gate:
GW4/RN5 passed, whereas GW8/RN5 and GW14/RN5 produced large
$\hat R_{\log A}$ excursions.  The current diagnostics are most consistent
with the red-noise/noise-policy block being the main blocker, but this has not
been isolated from duplicate-handling and Fourier-basis effects.  These tests
are therefore not Bayes factors and have no nested-sampling or
thermodynamic-integration evidence.

We also ran a refreshed exact-baseline local-ingestion gate on the public PTA
products.  This gate is read-only, uses ENTERPRISE loaders, and does not edit
timing-model files.  It separates local data availability from likelihood-policy
harmonization.

\begin{table}[H]
\caption{\label{tab:full-loader}Full public-PTA loader and noise-product gate.
PASS means that the staged par/tim or feather product loads through the local
standard loader; it is not a timing-level evidence calculation.}
\begin{ruledtabular}
\begin{tabular}{lcccc}
Product & expected & loaded & failures & status \\
\hline
NG15 feather route & 67 & 67 & 0 & PASS \\
EPTA DR2new+ & 25 & 25 & 0 & PASS \\
PPTA DR3 & 32 & 32 & 0 & PASS \\
MPTA 4.5 yr & 83 & 83 & 0 & PASS \\
InPTA DR1 NB & 14 & 13 & 1 & PARTIAL \\
InPTA DR1 WB & 14 & 0 & 14 & FAIL \\
\end{tabular}
\end{ruledtabular}
\end{table}

The refreshed manifest target contains 68 NANOGrav timing names, 25 EPTA
names, 32 PPTA names, 14 InPTA names, and 83 MPTA names.  The local MPTA
DataCentral partim refresh now matches the 83-pulsar target, but production use
still requires the exact duplicate-combination and noise-policy recipe.  InPTA
remains policy-blocked: the read-only diagnostics identify a fitted
\texttt{DMXR1} anomaly in the NB route and missing \texttt{FORMAT 1}/malformed
\texttt{C}-prefix rows in the WB route.  The direct-combination manifest audit
finds 222 input occurrences, 121 canonical pulsar groups, 56 duplicate groups,
two alias groups, and two canonical-name failures; all 56 duplicate or alias
groups are listed in
\nolinkurl{theory/5PTA_duplicate_policy_worklist_2026-04-25.md}.

\begin{table}[H]
\caption{\label{tab:timing-pilots}Mechanical ENTERPRISE timing-pilot gates.
These pilots test object construction and a single likelihood evaluation only;
they are not convergence tests, Bayes factors, or source-identification
results.}
\begin{ruledtabular}
\begin{tabular}{lcccc}
Pilot & pulsars & GW bins & RN bins & status \\
\hline
NG15 timing route & 8 & 4 & 0 & PASS \\
NG15+EPTA+PPTA & 12 & 4 & 0 & PASS \\
NG15+EPTA+PPTA & 12 & 8 & 5 & PASS \\
\end{tabular}
\end{ruledtabular}
\end{table}

The exact-baseline decision is therefore unchanged: no timing-level family
evidence is used in this Letter.  A production timing-level comparison must
first reproduce a selected public five-PTA baseline with the same
direct-combination, white-noise, and InPTA preprocessing policy; only then
should minimal family evidence be run.

\section*{S18. LSS Tomography Production Gate}

We also staged a separate LSS-correlated-anisotropy production gate.  Its first
science requirement is reproduction of the published NG15+2MPZ null before any
DESI or WISE$\times$SuperCOSMOS redshift-bin ORF is interpreted.  The current
gate therefore supplies only geometry and resource diagnostics.

\begin{table}[H]
\caption{\label{tab:lss-gate}LSS local production-gate status.  None of these
rows is an LSS evidence result.}
\begin{ruledtabular}
\begin{tabular}{lcc}
Gate & local result & interpretation \\
\hline
2MPZ input & 933447 valid rows & staged input \\
DESI/WISE$\times$SCOS ORFs & present & staged inputs only \\
NaMaster/MAP map gate & \texttt{pymaster} missing & environment blocker \\
low-$\ell$ 2MPZ fallback & PASS & deterministic fallback diagnostic \\
NG15+2MPZ published null & not reproduced & blocks LSS science claim \\
\end{tabular}
\end{ruledtabular}
\end{table}

The fallback low-$\ell$ 2MPZ gate uses the two reference slices
$0<z\le0.1$ and $0.1<z\le0.2$, a Galactic latitude cut
$|b|\ge20^\circ$, weighted monopole/dipole subtraction, and
$2\le\ell\le12$ truncation.  At \texttt{nside=64}, it gives NG15 pair-ORF
correlations with Hellings--Downs of $-0.103$ for the low-redshift slice and
$-0.212$ for the higher-redshift slice.  These values are useful for
debugging geometry and normalization, but they do not replace NaMaster C1
apodization, MASTER/MAP reconstruction, or a hypermodel likelihood.  DESI and
WISE$\times$SuperCOSMOS tomography therefore remain future production inputs
until the NG15+2MPZ published null (arXiv:2603.02110) is reproduced.

\FloatBarrier
\clearpage

\section*{S19. Minimal Local Verification Commands}

Run from the project root:
\begin{verbatim}
python3 code/gwb_templates.py
python3 -m py_compile code/prl_*.py
python3 code/prl_decisive_evidence_figure.py
python3 code/prl_reference_bridge_pipeline.py all --profile production --force
python3 code/prl_reference_bridge_pipeline.py p2seq --profile production
python3 code/prl_bridge_evidence_figure.py
python3 code/prl_ceffyl_plateau_diagnostic.py
python3 code/pta_identifiability_ppc.py
python3 code/smbhb_population_controls.py
python3 code/prl_final_stability_diagnostics.py
python3 code/manifest_v2_baseline_gate.py --tag 2026-04-25-local-refresh
python3 code/pta_full_loader_noise_tests.py
python3 code/pta_direct_combination_manifest_audit.py --inpta-band NB \
  --tag 2026-04-25-local-refresh
python3 code/inpta_loader_failure_diagnostic.py
python3 code/pta_timing_baseline_pilot.py --arrays NG15_TIMING EPTA PPTA \
  --max-per-array 4 --components-gw 8 --components-rn 5 \
  --include-red-noise --output-suffix 3array_4each_gw8_rn5
python3 code/lss_tomography_manifest.py
python3 code/lss_2mpz_lowell_reference_gate.py --nside 64 \
  --tag prod_nside64_lowell_update_20260425 --nulls 128 --seed 20260425
python3 code/fixed_red_sensitivity_experiments.py --mode duplicate \
  --steps 2000 --tag 2026-04-24_BC
python3 code/prl_evidence_ti_qmc_crosscheck.py
python3 code/prl_package_static_gate.py
\end{verbatim}

The package static gate writes
\nolinkurl{results/T2_NG15yr/prl_package_static_gate.json} and
\nolinkurl{results/T2_NG15yr/prl_package_static_gate.md}.

\end{document}
